Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-05-23 ms.qmd
See previous comment message

```{r}
#| label: future_clim
#| echo: false
#| warning: false
#| include: false

@@

@@

# Need to take a step back
  # 1. Why do we have NA in this data set? 
  # 2. Why are l95 and u95 for marine not working
  # 3. Apply to the posteriors, rather than summary.

@@

Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` populations). Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-preds). Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).

Projected changes in the opportunity for selection were highly variable across the globe, with some regions showing a decrease in the opportunity for selection, while others showing an increase (@fig-preds D). Out of the `r length(unique(all_pred2$match))` populations variance was predicted to decrease in `r `

```{r}
#| label: fig-preds
#| echo: false
#| warning: false
#| message: false
#| fig-cap: Model predictions for the expected change in acclimation $lnCVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms. Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).

>>>>

```{r, future_clim}
#| label: future_clim
#| echo: false
#| warning: false
#| include: false

@@

  # Lets now use the whole posterior distribtion instead. This is a little hacky because the object is complicated

  # First, lets merge the climate data with the predcitions, but here predcitions are not summarised. We have the entire posteior
    cols_select <- colnames(all_pred2_no_sum) %in% c(1:3200)

@@

  # Second, lets convert each estimate to lncvr 1 degree C insteda of 10
   all_pred2_no_sum2 <- all_pred2_no_sum %>%  
                        mutate_if(cols_select, lncvr_1c)

  # Third, lets multiply each estimate by the temperature change at that location. I've checked 4 different cells and they are calculated correctly.
    all_pred2_no_sum2[,cols_select]  <- all_pred2_no_sum2[,cols_select] * all_pred2_no_sum2$T_change

# Need to take a step back
  # 1. Why do we have NA in this data set? Thats because some species in the Future projections don't have data!
  # 2. Why are l95 and u95 for marine not working...no idea
  # 3. Apply to the posteriors, rather than summary. Working on this....

@@

Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` populations). Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-fig6). Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).

Projected changes in the opportunity for selection were highly variable across the globe, with some regions showing a decrease in the opportunity for selection, while others showing an increase (@fig-fig6 D). Out of the `r length(unique(all_pred2$match))` populations variance was predicted to decrease in `r `

```{r, fig-fig6}
#| label: fig-fig6
#| echo: false
#| warning: false
#| message: false
#| fig-cap: Model predictions for the expected change in acclimation $lnCVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms. Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).
